Report

### 2014-11-10 MSLLReport.tex
update in 11.10

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

@@

	\begin{frame}
		\frametitle{Maximum Entropy Models(2)}

>>>>

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{biblatex}
\bibliography{Domingos}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

@@

	\begin{frame}
		\frametitle{Maximum Entropy Models(2)}
		Here, we use binary feature function for feature selection.
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $x,y$ satisfy some condition}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
		In statistics, the empirical distribution is the cumulative distribution associated with the empirical measure of the sample.

		Let $\hat{p}(x,y)$ and $\hat{p}(x)$ to be defined as:
		$$\hat{p}(x,y) = \frac{count(x,y)}{N},\hat{p}(x) = \frac{count(x)}{N}$$
	\end{frame}
	\section{Distance and Divergence}
	\begin{frame}
		\frametitle{Distance}
		\textbf{Distance} satisfies four constraints which \text{Divergence} may no satisfy.
		\begin{itemize}
			\item \textbf{Non-negativity:} $\forall x,y,\quad d(x,y) \ge 0$
			\item \textbf{Non-degeneracy:} $d(x,y)=0 \Leftrightarrow x=y$
			\item \textbf{Symmetry:} $\forall x,y, \quad d(x,y)=d(y,x)$
			\item \textbf{Triangularity:} $\forall x,y,z \quad d(x,z)\leq d(x,y)+d(y,z)$
		\end{itemize}
		\begin{figure}
			\pgfimage[width=4cm]{"image/29.png"}
		\end{figure}	
	\end{frame}

	\begin{frame}
		\frametitle{Distance(2)}
		In the \textbf{Euclidean space} $\mathbb{R}^n$ ,the distance between two point can be given by \textbf{Minkowski distance}.(When p=2, it is equivalent the \textbf{Euclidean distance} and when p=1, it is equivalent to \textbf{Manhattan distance} ) Other distance, based on norms, are sometimes used instead.
		\begin{itemize}
			\item 1-norm distance  $= \sum_{i=1}^{n}|x_i-y_i|$
			\item 2-norm distance  $= \left(\sum_{i=1}^{n}|x_i-y_i|^2\right)^{1/2}$
			\item p-norm distance  $=  \left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
			\item $\infty$ norm distance $=\lim\limits_{p\rightarrow\infty}\left(\sum_{i=1}^{n}|x_i-y_i|^p\right)^{1/p}$
		\end{itemize}
		If we care about the direction of the data rather than the magnitude, then using the \textbf{cosine distance} is a common approach. 
		$$\cos \theta = \frac{A\cdot B}{\|A\|\|B\|}$$
	\end{frame}

	\begin{frame}
		\frametitle{Distance(3)}
		\textbf{Why is Euclidean distance not a good metric in high dimensions?}
		\begin{itemize}
			\item 
		\end{itemize}
		Here is text
		\fullcite{Domingos}
